\documentclass[11pt, a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage{geometry}
\usepackage{lmodern}
\usepackage{amsmath}

% Adjust page margins
\geometry{
    a4paper,
    left=1in,
    right=1in,
    top=1in,
    bottom=1in,
}

% Remove page numbering
\pagestyle{empty}

\begin{document}

\begin{center}
    \Large\bfseries Ryan Chen Rui Yang\\
\end{center}

\vspace{1mm} % Vertical space

\begin{center}
    +65 97322077 \textbullet{} ryanchen@live.com.sg \textbullet{} linkedin.com/in/ryanno3o
\end{center}

\vspace{6mm} % Vertical space before the main text

\noindent
To whomever it may concern,

\vspace{5mm} % Vertical space after salutation

% --- PARAGRAPH 1: PERSONALITY ---
\noindent
I am an independent individual, driven by an intense curiosity to deconstruct complex ideas and systems, so as to fully understand the intricate dynamics of what I'm doing. I'm known as someone with a proactive and self-reliant personality, and find joy in exploring challenges, as well as identifying opportunities for improvement. I thrive in collaborative environments, taking the time to better learn about my colleagues,  while being able to comfortably take ownership of tasks and see it through to completion. I strongly believe this unique combination of a reflective, growth-oriented mindset and a drive for creative problem-solving would be a strong asset to any dynamic and forward-thinking team.

\vspace{5mm}

% --- PARAGRAPH 2: EDUCATION + SOFT SKILLS ---
\noindent
My pursuit of a Computer Science degree at the National University of Singapore, while rigorous in logical reasoning and adaptive problem-solving, has taught me how to manage studies, social life, and work opportunities altogether. This process has sharpened not only my analytical skills, but also my mental capacity for time management and improvisation. Moreover, this academic foundation has equipped me with a powerful and flexible framework for the thorough analysis, collaboration, and data-driven decision-making fundamental to roles that require more than just technical knowledge, but also creative insight.

\vspace{5mm}

% --- PARAGRAPH 3: WORKPLACE TECHNICAL SKILLS ---
\noindent
So far, I had the opportunity to translate these skills into practical results during my internship at the Home Team Science and Technology Agency (HTX). My superiors have pointed out that I am adept at quickly mastering new tools to solve pressing business problems. For instance, I took the initiative to automate a critical data-handling process using Power Automate, delivering a working solution that enhanced operational efficiency. Additionally, the development of my department's Intranet website demonstrated my meticulous attention to detail and my commitment to producing polished, high-quality products. This experience, which involved proactively organising content and performing rigorous quality checks, directly mirrors the high standards and dedication required to perform well at work. My proven ability to operate independently, manage multiple assignments, and deliver quality outcomes, effectively underscores my potential to make meaningful and effective contributions from day one.

\vspace{5mm}

% --- CLOSING ---
\noindent
I'm hereby excited by the opportunity to learn more and discuss how my unique blend of technical skill and personal drive can not only contribute to a productive workplace, but also foster an engaging and dynamic environment.

\vspace{5mm}

\noindent
Yours sincerely, \\
\noindent
Ryan Chen

\end{document}